Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
rewordings

\section{Abstract Analysis}
\label{sec:analysis}

@@

However, template variables tell us exactly where this kind of change can happen. The only way in which the spine routers depend on anything non-local is in the match on prefix template variables. Instead, we can associate a new unique community tag for template variable {\small \$GP} and then replace each match on {\small \$GP} with a test on the new community tag. The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can just match the community tag.

@@

The \sysname compiler is implemented in approximately 9500 lines of F\# code. The compiler accepts both concrete and abstract topologies and will generate configurations for open-source Quagga routers by default. The abstract analysis uses $\nu$Z~\cite{z3opt} to test validity and to minimize variables subject to the annotated constraints. Since the analysis typically calls the SMT solver many times with relatively simple optimization problems, we use a short timeout of 200ms.

@@

\begin{figure}[t!]
  \begin{center}
      \begin{tabular}{| l | c | c | c |}
      \hline
      \textbf{Topology} & \textbf{Fixed} & \textbf{Reachability} & \textbf{K-paths} \\ \hline
      Fattree~\cite{fattree} & & \cmark & \cmark  \\ \hline
      Facebook~\cite{facebook-fattree} & & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & & \cmark & \cmark \\ \hline
      VL2~\cite{vl2-fattree} & & & \\ \hline
      BCube~\cite{bcube} & $k$ & \cmark & \xmark \\ \hline
      Dcell~\cite{dcell} & $k$ & \cmark & \xmark \\ \hline
         %& HCN & $h$ & \cmark & \xmark \\
      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark \\ \hline
      Hypercube & $N$ & \cmark & \cmark \\ \hline
      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark \\ \hline
      \end{tabular}
  \end{center}
  \caption{Abstract Analysis Precision.}
  \label{fig:analysis-precision}
\end{figure}

@@

We evaluate the expressiveness and precision of our abstract analysis on a range of different network topologies found in network literature and in production networks. The analysis is precise if it finds a tight lower-bound on the fault-tolerance (\IE, there is actually a concrete network with that fault tolerance).
For each topology in Figure~\ref{fig:analysis-precision} we define a suitable abstraction. Since many topologies have tunable parameters (\EG, the recursion depth $k$ for the Dcell topology), we list all such parameters that are fixed for the abstraction. We implement a shortest path routing policy over the topology and record the precision of the analysis in terms of whether or not it is able to accurately prove reachability and/or the correct number of disjoint paths between all pairs of nodes.

@@

Hypercube variants can be used as an alternative to Clos-style topologies for networks with high-radix (port density) routers. The HyperX~\cite{hyperx} topology can be viewed as a generalization of the hypercube and butterfly topologies, which includes parameters $L$ for the lattice dimension of the network, and $S_i$ for the node multiplicity of each dimension $i$.
%$K_i$ for the bandwidth of links for each dimension, 
%and $T$ for the number of terminal nodes (servers) connected to each router. 
For a fixed number of dimensions $L$, we abstract each full mesh of $S_L$ nodes into its own abstract node. The $S_{x-1}$ groups of abstract nodes can be captured using pods of the abstract $S_x$ nodes. For all hypercube variants, the abstract analysis is precise.

@@

For both the networks, the abstract compilation starts off slightly slower than concrete compilation for small topologies due to the overhead of the abstract analysis for fault-tolerance. However, as the size of the topology increases, abstract compilation becomes orders of magnitude faster than concrete compilation. In all cases for both networks, abstract compilation takes less than 10 seconds to complete.

Figure~\ref{fig:abstract-breakdown} shows the relative time taken by each phase of abstract compilation. Notably, the abstract analysis takes the majority of the time, however the analysis does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost. In particular, the number of calls to $\nu$Z remains constant the across topology size. The seesaw behavior for the data center networks results from differences in time taken by $\nu$Z to minimize similar constraints with different values.

>>>>

\section{Fault-tolerance Analysis}
\label{sec:analysis}

@@

However, template variables tell us exactly where this kind of change can happen. The only way in which the spine routers depend on anything non-local is in the match on prefix template variables. Instead, we can associate a new unique community tag for template variable {\small \$GP} and then replace each match on {\small \$GP} with a test on the new community tag. The new ToR must now simply attach the new community tag to advertisements for its prefixes so downstream routers can just match the community tag. Figure~\ref{fig:bgp-configs} (right) shows the templates after the transformation.

@@

The \sysname compiler is implemented in approximately 9500 lines of F\# code. The compiler accepts both concrete and abstract topologies and will generate configurations for open-source Quagga routers by default. The fault-tolerance analysis uses $\nu$Z~\cite{z3opt} to test validity and to minimize variables subject to the annotated constraints. Since the analysis typically calls the SMT solver many times with relatively simple optimization problems, we use a short timeout of 200ms.

@@

\begin{figure}[t!]
  \begin{center}
      \begin{tabular}{| l | c | c | c |}
      \hline
      \textbf{Topology} & \textbf{Fixed} & \textbf{Reachability} & \textbf{K-paths} \\ \hline
      Fattree~\cite{fattree} & & \cmark & \cmark  \\ \hline
      Facebook~\cite{facebook-fattree} & & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & & \cmark & \cmark \\ \hline
      VL2~\cite{vl2-fattree} & & & \\ \hline
      BCube~\cite{bcube} & $k$ & \cmark & \xmark \\ \hline
      Dcell~\cite{dcell} & $k$ & \cmark & \xmark \\ \hline
         %& HCN & $h$ & \cmark & \xmark \\
      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark \\ \hline
      Hypercube & $N$ & \cmark & \cmark \\ \hline
      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark \\ \hline
      \end{tabular}
  \end{center}
  \caption{Fault-tolerance analysis precision.}
  \label{fig:analysis-precision}
\end{figure}

@@

We evaluate the expressiveness and precision of our fault-tolerance analysis on a range of different network topologies found in network literature and in production networks. The analysis is precise if it finds a tight lower-bound on the fault-tolerance (\IE, there is actually a concrete network with that fault tolerance).
For each topology in Figure~\ref{fig:analysis-precision} we define a suitable abstraction. Since many topologies have tunable parameters (\EG, the recursion depth $k$ for the Dcell topology), we list all such parameters that are fixed for the abstraction. We implement a shortest path routing policy over the topology and record the precision of the analysis in terms of whether or not it is able to accurately prove reachability and/or the correct number of disjoint paths between all pairs of nodes.

@@

Hypercube variants can be used as an alternative to Clos-style topologies for networks with high-radix (port density) routers. The HyperX~\cite{hyperx} topology can be viewed as a generalization of the hypercube and butterfly topologies, which includes parameters $L$ for the lattice dimension of the network, and $S_i$ for the node multiplicity of each dimension $i$.
%$K_i$ for the bandwidth of links for each dimension, 
%and $T$ for the number of terminal nodes (servers) connected to each router. 
For a fixed number of dimensions $L$, we abstract each full mesh of $S_L$ nodes into its own abstract node. The $S_{x-1}$ groups of abstract nodes can be captured using pods of the abstract $S_x$ nodes. For all hypercube variants, the fault-tolerance analysis is precise.

@@

For both the networks, the abstract compilation starts off slightly slower than concrete compilation for small topologies due to the overhead of the fault-tolerance analysis. However, as the size of the topology increases, abstract compilation becomes orders of magnitude faster than concrete compilation. In all cases for both networks, abstract compilation takes less than 10 seconds to complete.

Figure~\ref{fig:abstract-breakdown} shows the relative time taken by each phase of abstract compilation. Notably, the fault-tolerance analysis takes the majority of the time, however the analysis does not depend on the number of concrete nodes in the network, and thus is largely a fixed cost. In particular, the number of calls to $\nu$Z remains constant the across topology size. The seesaw behavior for the data center networks results from differences in time taken by $\nu$Z to minimize similar constraints with different values.
